Data Encryption Standard Implementation 4003-482-01 RIT

### 2010-05-06 paper/paper.tex
Started Revised Runtime Analysis

\section{Revised Runtime Analysis}

\section{Developers manual}

>>>>

\section{Revised Runtime Analysis}
  One of the major changes was the f (feistel) function. It went from 23\% to 43\% of the total runtime.  This change is largely because we removed the mixer function. Mixer accounted for 41\% of the runtime, 63\% of mixer's calls were from feistel.  From this we can deduce that 26\% out of the 41\% was directly due to f, and we could say that f really caused 23\% + 26\% = 49\% of the runtime.  From this we can see that the f function's overall contribution to execution time went down without removing any of its duties. 
\section{Developers manual}
